Evaluating KNN, SVR, ANN, XGBoost Regressor, Linear Regression, and Random Forest Models for Dengue Case Prediction: A Comparative Study

### 2024-12-10 paper/main.tex
final modifications

\subsubsection{Data Integration and Preprocessing}
The dengue case data was integrated with the weather data to create a comprehensive dataset\footnote{For reference of the complete dataset:\\ 
	\url{https://github.com/HENERALPEPITO/ML-miniproject/tree/main/datasets}}, aligning the data based on corresponding timeframes. The dataset undergoed a cleaning process to address any missing values, outliers, and inconsistencies to ensure its accuracy and reliability. To ensure that all features and the target variable were on the same scale, a MinMaxScaler was applied to normalize both the input features (rainfall, temperature, humidity) and the target variable (dengue cases). To enhance the quality of the data and minimize the impact of random short-term fluctuations, moving averages was applied to selected columns, including rainfall, humidity, temperature, and cases. This approach will help to filter out 'noise' and provide a clearer representation of the underlying trends.

@@

@@

>>>>

\subsubsection{Data Integration and Preprocessing}
The dengue case data was integrated with the weather data to create a comprehensive dataset\footnote{For reference of the complete dataset:\\ 
	\url{https://github.com/HENERALPEPITO/ML-miniproject/tree/main/datasets}}, aligning the data based on corresponding timeframes. The dataset undergoed a cleaning process to address any missing values, outliers, and inconsistencies to ensure its accuracy and reliability. To enhance the quality of the data and minimize the impact of random short-term fluctuations, moving averages was applied to selected columns, including rainfall, humidity, temperature, and cases. This approach will help to filter out 'noise' and provide a clearer representation of the underlying trends. To ensure that all features and the target variable were on the same scale, a MinMaxScaler was applied to normalize both the input features (rainfall, temperature, humidity) and the target variable (dengue cases).

@@

From the plot, we observe that all models, except the KNN model, closely follow the trends, particularly in capturing the peaks of dengue cases. This alignment indicates that the models identified the temporal dynamics and surges in dengue outbreaks from the dataset.

@@

\section{Recommendations}

For future research, it is recommended to divide the dataset by year and perform training and testing splits within each year. This approach ensures that the predictive models are trained and evaluated using data reflective of the seasonal and temporal patterns specific to that year. By doing so, the models can capture short-term trends more effectively, which is critical for accurate near-future predictions.

Additionally, this method aligns with the practical application of dengue case prediction. For example, when predicting the number of cases for tomorrow, recent data holds more relevance and predictive power compared to data from several years ago. Incorporating more recent patterns helps models adapt to potential changes in factors such as weather patterns, population behavior, and vector dynamics, ensuring more reliable forecasts.
